% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage[colorlinks=true]{hyperref}
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

\begin{document} 

\name{Felix R. Chern\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{\bf  PRESENT ADDRESS\\5F. No.19, Ln.86, Sec.3, \\XingSheng S. Rd.,
Taipei 12180\\(886) 928-055225}
\address{\bf  PERSONAL SITES \\ \url{http://idryman.org}\\
\url{http://search.cpan.org/~dryman/}\\
\url{http://www.linkedin.com/profile/view?id=139702533}\\
\url{https://github.com/dryman} \\
}
                                  
\begin{resume}

\section{JOB OBJECTIVE}          
Looking for an iOS development job.
 
\section{EDUCATION}          
    Mechanical Engineering, National Taiwan University \\
    Bachelor degree, June 2011\\
    G.P.A. 3.3/4.0\\
    Self educated in computer science and software engineering \\

 
\section{EXPERIENCE}
   \vspace{-0.1in}	
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Research Assistant} \>Institute of Information Science\>Fall 2011-Present\\
                             \>Academia Sinica
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    I'm working under "Open Information System for Disaster Management
    (OpenISDM)" project which targeted on designing information system to reduce
    and repair Taiwan disasters. I am the project website constructor and
    administrator. I response for a crowdsourcing project and iOS app
    development.
    
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf System Administrator } \>Biomimetics, Energy, \> Spring 2010 - Fall 2011\\
    {(still a student)}   \>and Microfluid (BEAM) Laboratory\\
                          \> National Taiwan University
   \end{tabbing}\vspace{-20pt}
   I worked at BEAM lab as a Linux system administrator and build up scientific
   development environment of commercial and open source softwares. At the time
   I also collaborate with Mathematic department for numerical calculation
   studies and medical imaging.
   \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf Undergraduate research} \>Department of Mathematics\> Fall 2010 - Fall 2011\\
                          \>National Taiwan University
   \end{tabbing}\vspace{-20pt}
   I am the second author of "Ultrafast image reconstruction of a dual-head PET
   system by use of CUDA architecture,” supervised by Professor Weichung Wang.
   \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf Undergraduate research} \>National Science Council\> 2009-2010 \\
   \end{tabbing}\vspace{-20pt}
   NSC Undergraduate Research Project, “Image Recognition for Fish Motion,”
   supervised by Professor Jing-Tang Yang, Department of Mechanical Engineering.
   After this project, I went to professor Yang's laboratory as system
   administrator.


\section{COMPUTER SKILLS}          
  One of the Perl CPAN Authors. (\url{http://search.cpan.org/~dryman}) \\
  Objective-C programming, on Mac and iOS. \\
  Ruby programming, mostly writing plugins for Jekyll blogging system.\\
  Matlab and bridge to C/Cpp. It is best to solve numerical problems in Matlab.\\
  Nvidia CUDA. We used this to solve medical imaging problems.\\
  JQuery, nodejs and javascript. I made a push notification demo with it.\\
  Common Lisp and Clojure (my recent hobby.)\\

\section{HIGHLIGHTED OPEN SOURCE PROJECTS}
  \url{https://github.com/dryman} \\
  \url{http://search.cpan.org/~dryman} \\


  Lingua::ZH::MMSEG Mandarin Chinese segmentation. In my current job of
  crowdsourcing project, we need to process Chinese text and do keyword
  extraction. Linua::ZH::MMSEG is the key part of the process. 

  CangJieX CangJie Chinese input method for osx. I made this input method for
  myself, because osx's input method sucks.

  NodeJS jquery mobile demo. A simple demo for sending notification actively to
  multiple browser clients.

  \href{http://www.idryman.org/blog/2012/04/04/jekyll-graphviz-plugin/} {Jekyll graphviz plugin.}
  Generate eye stunning graphs right in Jekyll markdown text.

  \href {http://www.idryman.org/blog/2012/04/05/jekyll-octopress-hacker-news-plugin/} {Jekyll hacker news plugin.}
  Add a hacker news button on Jekyll blog post.
 
 
\section{HONORS AND AWARDS}          
  Third place of undergraduate research competition, North Center of
  Inter-Science Education Program, ``Prey and Predator ODE Model Simulation'',
  supervised by Professor Hung-Chi Kuo, Department of Atmospheric Sciences,
  National Taiwan University, 2007. \\
  Scholarship, Formosan Summer School on Logic, Language, and Computation Summer
  School, National Taiwan University, 2010.\\
  Third place of competition for Matrix Computation Benchmark in High
  Performance Computation Summer School at KTH (Royal Institute of Technology),
  Sweden, 2010.\\

\section{INTERNATIONAL CONFERENCE PAPER}
  YuKai Hung, Felix R. Chern, Weichung Wang, and Cheng-Ying Chou, “Ultrafast
  image reconstruction of a dual-head PET system by use of CUDA architecture,”
  Lake Buena Vista, Florida, USA, 2011.
 
\section{COMMUNITY ACTIVITIES}
Chupei Perl (Perl Developer Club)\\
CocoaHeads Taipei\\
Rails Tuesday\\
RGBA Taipei (web design and development club)\\

\section{CAMPUS INVOLVEMENT}
NTU Magic Club\\
NTU Chorus\\

 
\end{resume}
\end{document}
